\documentclass{article}
\usepackage{xargs}% Uniquement pour être sur que je ne me suis pas trompé dans l'appel au sein du .dtx
\usepackage{ledmac}

\begin{document}
\newcommand{\toto}[1]{#1}
%\numberonlyfirstinline[A]
\numberonlyfirstinline
\beginnumbering
\renewcommand{\parafootftmsep}{$||$}
\renewcommand*{\symplinenum}{$||$}
\footthreecol{B}
\foottwocol{C}
\footparagraph{D}
\pstart



A \edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{ \Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{ \Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{ \Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{ \Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{ \Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{ \Afootnote{The date was July 16, 1954.}}
\pend
\pstart
B \edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{ \Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{ \Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{ \Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{ \Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{ \Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{ \Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{ \Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{ \Bfootnote{The date was July 16, 1954.}}
\pend

\pstart
C \edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{ \Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{ \Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{ \Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{ \Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{ \Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{ \Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{ \Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{ \Cfootnote{The date was July 16, 1954.}}
\pend

\pstart
D \edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{ \Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{ \Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{ \Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{ \Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{ \Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{ \Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{ \Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{ \Dfootnote{The date was July 16, 1954.}}
\pend
\endnumbering

\end{document}