\documentclass{book}
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage[series={A}]{eledmac}
\usepackage{eledpar}

\begin{document}

\beforeeledchapter

\begin{pages}

\begin{Leftside}
\beginnumbering

\pstart[\chapter{The Creed}]
s
\pend

\pstart
\centerline{I scorn the Daevas.}
\pend

\numberpstarttrue
\autopar

I choose to be a Mazda-worshipper like Zarathushtra,\\
against the Daevas, guided by Ahura,\\
praising the Amesha Spentas, worshipping the Amesha Spentas. I ascribe all good to Ahura Mazda, Asha-endowed, splendid, glorious; whose is the Cow, whose is Asha, whose is the light, whose lands of freedom are filled with light.

I choose Life-giving Devotion, Spenta Armaiti, the good one. I praise the Cow, and hereby pledge to protect her from theft and violence; I praise the settlements of Mazda-worshippers, and hereby pledge to protect them from damage and plunder.

You give freedom of movement and freedom of dwelling for those with homesteads, to those who dwell upon this earth with their cattle, in reverence for Asha.  I praise all this. I shall never damage or plunder Mazda-worshipping homes, not even to save my life or limb.

I reject the company of the Daevas, who have nothing good to give, whose work produces no Asha, who give evil gifts; the most lying of all beings, the foulest of all beings, who of all beings have the least to offer.  I reject the company of the Daevas and sorcerers, and those possessed by them; I reject the company of all that support the Lie.

And thus again and again, Ahura Mazda taught Zarathushtra in all discussions, in all meetings, in which they conversed,

And thus again and again, Zarathushtra rejected the company of the Daevas, in all discussions, in all meetings, in which Ahura Mazda and Zarathushtra conversed,

And thus I also reject, as a Mazda-worshipper in the tradition of Zarathushtra, the company of the Daevas, even as he, the Asha-endowed Zarathushtra, would reject them.

By the choice of the waters, the choice of the plants, the choice of the beneficial  Cow; by the choice of Ahura Mazda who created the Cow and the Asha-endowed Man; by the choice of Zarathushtra, by the choice of Kavi Vishtaspa, by the choice of Frashaostra and Jamaspa; by the choice of each of the Saoshyants, producing what is real and Asha-endowed; by this same choice, I am a Mazda-worshipper.

I choose to be a Mazda-worshipper in the tradition of Zarathushtra, having presented myself as a praiser thereof. I pledge myself to the well-thought thought; I pledge myself to the well-spoken word; I pledge myself to the well-done deed.

I pledge myself to the Mazda-worshipping religion, which throws off shackles and causes weapons to be laid down; which teaches self-reliance; which conforms to Asha; which, of those which are and those that shall be, is the greatest, best, and most beautiful; worthy of Ahura Mazda and Zarathushtra. I ascribe all good to Ahura Mazda. Thus do I pledge myself to the Mazda-worshipping religion.

\endnumbering
\end{Leftside}

\begin{Rightside}
\beginnumbering

\pstart[\chapter{Fravarānē}]
s
\pend

\pstart
\centerline{Nāismī Daēvō.}
\pend

\numberpstarttrue
\autopar

Fravarānē Mazdayasnō Zarathushtrish,\\
vīdaēvō Ahura-tkaēshō,\\
staotā Ameshanąm Speñtanąm yashtā Ameshanąm Speñtanąm, Ahurāi Mazdāi vanghavē vohumaitē vīspā vohū cinahmī Ashāunē raēvaitē hvarenanguhaitē yā-zī cīcā vahishtā yenghē Gāush yenghē Ashem yenghē raocå yenghē raocēbīsh rōithwen hvāthrā.

Speñtąm Ārmaitīm vanguhīm verenē, hā-mōi astū, us Gēush stuyē tāyāatcā hazanghatcā, us Mazdayasnanąm vīsąm zyānayaēcā vīvāpatcā.

Ferā manyaēibyō rånghē vasē-yāitīm vasē-sheitīm yāish upairī āya-zemā gaobīsh shyeñtī, nemanghā Ashāi uzdātå paitī avat stuyē, nōit ahmāt āzyånīm nōit vīvāpem xshtā Māzdayasnīsh aoi vīsō nōit astō nōit ushtānahē cinmānī. 

Vī Vaēvāish akhāish avanghūsh anaretāish akō-dābīsh sarem mruyē hātąm draojishtāish hātąm paoshishtāish hātąm avanghutemāish vī daēvāish vī daēvavatbīsh vī yātush vī yātumatbīsh vī kahyācīt hātąm ātarāish vī manēbīsh vī vacēbīsh vī shyaothanāish vī cithrāish, vī zī anā sarem mruyē yathanā dregvātā rąxshayañtā. 

Athā athā cōit Ahurō Mazdå Zarathushtrem adhaxshayaētā vīspaēshū ferashnaēshū vīspaēshū hañjamanaēshū yāish aperesaētem Mazdåscā Zarathushtrascā, 

Athā athā cōit Zarathushtrō Daēvāish sarem vyāmrvītā vīspaēshū ferashnaēshū vīspaēshū hañjamanaēshū yāish aperesaētem Mazdåscā Zarathushtrascā,

Athā azēmcīt yō Mazdayasnō Zarathushtrish Daēvāish sarem vīmruyē yathā anāish vyāmrvītā yē Ashavā Zarathushtrō. 

Yā-varanā āpō yā- varanā urvarå yā-varanā gāush hudå yāvaranō ahurō mazdå yē gąm dadā yē narem ashavanem yāvaranō as zarathushtrō yāvaranō kavā vīshtāspō yāvaranā ferashaoshtrā jāmāspā yāvaranō kascīt saoshyañtąm haithyāvareząm ashāunąm tā varenācā tkaēshācā (rāspī,) mazdayasnō ahmī! 

Mazdayasnō Zarathushtrish fravarānē, āstūtascā fravaretascā. Āstuyē humatem manō āstuyē hūxtem vacō āstuyē hvarshtem shyaothanem. 

Āstuyē daēnąm māzdayasnīm fraspāyaoxedhrąm nidhāsnaithishem hvaētvadathąm ashaonīm yā hāitinąmcā būshyeiñtinąmcā mazishtācā vahishtācā sraēshtācā yā āhūirish zarathushtrish, ahurāi mazdāi vīspā vohū cinahmī. aēshā astī daēnayå māzdayasnōish āstūitish!! 

\endnumbering
\end{Rightside}

\end{pages}
\Pages

\end{document}