\documentclass{article}
\usepackage{xunicode,fontspec}
\usepackage{xargs}% Uniquement pour être sur que je ne me suis pas trompé dans l'appel au sein du .dtx
\usepackage{ledmac}

\begin{document}
\lemmaseparator{>}
\beforenumberinfootnote[A]{2.5em}
\afternumberinfootnote[A]{2.5em}
\beginnumbering
\footthreecol{B}
\foottwocol{C}
\footparagraph{D}
\pstart



A \edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{\Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{\Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{\Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{\Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{\Afootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Afootnote{Jones.}} on Tuesday.}{\Afootnote{The date was July 16, 1954.}}
\pend
\pstart
B \edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{\Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{\Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{\Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{\Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{\Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{\Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{\Bfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Bfootnote{Jones.}} on Tuesday.}{\Bfootnote{The date was July 16, 1954.}}
\pend

\pstart
C \edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{\Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{\Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{\Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{\Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{\Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{\Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{\Cfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Cfootnote{Jones.}} on Tuesday.}{\Cfootnote{The date was July 16, 1954.}}
\pend

\pstart
D \edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{\Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{\Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{\Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{\Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{\Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{\Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{\Dfootnote{The date was July 16, 1954.}}\edtext{I saw my friend \edtext{Smith}{\Dfootnote{Jones.}} on Tuesday.}{\Dfootnote{The date was July 16, 1954.}}
\pend
\endnumbering

\end{document}