\documentclass[11pt,twoside]{book}

\usepackage{fontspec}
\usepackage{xunicode}
\setmainfont[]{Palatino}
\usepackage[parapparatus]{reledmac}
\usepackage[shiftedpstarts]{reledpar}

\setlength{\columnrulewidth}{0.4pt}

\Xarrangement[A]{paragraph}
\Xarrangement[B]{paragraph}
\Xarrangement[C]{paragraph}
\Xarrangement[D]{paragraph}

\newcommand{\choiceline}[2]{\linenum{|#1|#2||#1|#2}}
\sublinenumberstyle{alph}
\let\fullstop\relax

\setlength{\parindent}{0pt}
\setstanzaindents{0,0,0,0}
\setcounter{stanzaindentsrepetition}{0}
\numberstanzatrue

\Xstanza
\Xstanzaseparator{.}
\setRlineflag{}

\hidenumberingonrightpage
\firstlinenumR{100000}
\lineation{page}
\firstlinenum{1}
\linenumincrement{1}
\firstsublinenum{1}
\sublinenumincrement{1}


\begin{document}

\begin{pages}
\begin{Leftside}
\beginnumbering
  \autopar

\skipnumbering
\centering{||} O{||} \textit{avighnam astu}{||} O{||}

\noindent{}\edtext{saṅ}{\Bfootnote{em.; sa LOr}} saṅgrahakāri sira movus{|} liṅnira{|}

\begin{astanza}
 \setlength{\leftskip}{15mm}\setlength{\rightskip}{15mm}\itshape\hidenumbering \edtext{śūnyaś}{\choiceline{1}{1}\Afootnote{em.; śūnya A}}  ca \edtext{nirbbāṇādhikaḥ{|} śivāṅgatve}{\linenum{|2|1||2|2|}\Afootnote{em; nirbbhāṇādhika{|} śśivaṅgatve A, B}} nirīkṣyate{|}&
\setlength{\leftskip}{15mm}\setlength{\rightskip}{15mm}\itshape\hidenumbering kutaḥ tadvākyam atulaṁ{|} śrutvā devo \edtext{’vatiṣṭhati}{\Afootnote{em; vatiṣṭha{|} ca A, B}} {||} \normalshape 1.2\&[ ]
\end{astanza}

nāhan takvanaknaniṅ hulun ri bhaṭāra{|} hana ya pada śūnya{|} ya sinaṅguh ka\-mo\-kṣan{|} ṅa{|} viśeṣa ya{|} ya śiva ṅaranya{|} \textit{nirīkṣyate}{|} katon pva ya de saṅ \edtext{yogīśvara}{\lemma{\ldots{}gīśvara}\Cfootnote{B om.}}{|} sājñā bhaṭāra{|} an maṅkana kottamaniṅ vuvus saṅ ṛṣi{|} ya ta kaṛṅĕ de bhaṭāra{||} 1.2

\textit{\edtext{kenopāyena bhagavan}{\choiceline{25}{1}\Afootnote{em.; meyopāyena bhagavān LOr}\Dfootnote{unmetrical (\textit{bha-vipulā} with short second syllable)}}}{|}\textit{sukhayogasya lakṣaṇaṁ}{|} \edtext{nihan}{\Bfootnote{conj.; nāhan A}} takvananiṅ hulun ri kita bha\-ṭā\-ra{|} ndya kunaṅ \edtext{upāyanikā}{\Bfootnote{corr.; opāyanikā A}} saṅ paṇḍita{|} mataṅyan kapaṅguhāvaknikaṅ sukhādhyātmika{||} 10.25

\endnumbering

\end{Leftside}

    \begin{Rightside}
    \beginnumbering

{\centering\pstart Everything works here \pend}

\autopar

Everything works here:

\begin{astanza}
\setlength{\leftskip}{15mm}\setlength{\rightskip}{15mm}\itshape Everything works here. Everything works here. Everything works here. Everything works here. Everything works here.\&[ ]
\end{astanza}

Everything works here. Everything works here. Everything works here. Everything works here. Everything works here. Everything works here. Everything works here. Everything works here. Everything works here. Everything works here. (1.2)

Everything works here. Everything works here. Everything works here. Everything works here. Everything works here. Everything works here. Everything works here 10.10

    \endnumbering
        \end{Rightside}

\end{pages}
\Pages

\end{document}
