\documentclass[12pt,a4paper]{book}
\usepackage[english,polutonikogreek]{babel}
\usepackage[iso-8859-7]{inputenc}
\usepackage{eledmac}
\usepackage{eledpar}

\lineation{pstart}

\footparagraph{A}
\footparagraph{B}
\footparagraph{C}
\numberpstarttrue
\numberonlyfirstinline[A]
\numberonlyfirstinline[B]
\numberonlyfirstinline[C]

\begin{document}
\begin{pairs}
\begin{Leftside}
\beginnumbering
\pstart
Περι \edtext{<ερμηνείας}{\Afootnote{\textlatin{this variant should be printed with NO paragraph number 1}}}
\pend
\setcounter{pstartL}{1}
\pstart
<Ομώνυμα λέγεται <~ων \edtext{>όνομα}{\Afootnote{\textlatin{this variant should be printed under paragraph number 1, not 2}}} μόνον κοινόν, <ο δε κατα το>ύνομα λόγος τ~ης ο>υσίας <έτερος, ο<~ιον ζ~ω|ον <ό τε >άνθρωπος και το γεγραμμένον; τούτων γαρ >όνομα μόνον κοινόν, <ο δε κατα το>ύνομα λόγος τ~ης ο>υσίας <έτερος. <Ομώνυμα λέγεται <~ων >όνομα μόνον κοινόν, <ο δε κατα το>ύνομα λόγος τ~ης ο>υσίας <έτερος, ο<~ιον ζ~ω|ον <ό τε >άνθρωπος και το γεγραμμένον; τούτων γαρ >όνομα μόνον κοινόν, <ο δε κατα το>ύνομα λόγος τ~ης ο>υσίας <έτερος.
\pend
\pstart
<Ομώνυμα λέγεται <~ων \edtext{>όνομα}{\Afootnote{\textlatin{this variant should be printed under paragraph number 2, not 3}}} μόνον κοινόν, <ο δε κατα το>ύνομα λόγος τ~ης ο>υσίας <έτερος, ο<~ιον ζ~ω|ον <ό τε >άνθρωπος και το γεγραμμένον; τούτων γαρ >όνομα μόνον κοινόν, <ο δε κατα το>ύνομα λόγος τ~ης ο>υσίας <έτερος. <Ομώνυμα λέγεται <~ων >όνομα μόνον κοινόν, <ο δε κατα το>ύνομα λόγος τ~ης ο>υσίας <έτερος, ο<~ιον ζ~ω|ον <ό τε >άνθρωπος και το γεγραμμένον; τούτων γαρ >όνομα μόνον κοινόν, <ο δε κατ`α το>ύνομα λόγος τ~ης ο>υσίας <έτερος.
\pend
%\numberpstartfalse
\endnumbering
\end{Leftside}

\begin{Rightside}
\selectlanguage{english}
\beginnumbering
\pstart
English Title
\pend
\setcounter{pstartR}{1}

\pstart
This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample.
\pend
\pstart
This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample. This is just a test sample.
\pend
%\numberpstartfalse
\endnumbering
\end{Rightside}
\end{pairs}
\makeatletter
\eledmac@warning{\list@pstartL@pc}%
\Columns
\end{document}