
 \documentclass[11pt]{article}
\title{Turkish Embassy Letters}
\author{ed. Rebecca Chung}
\usepackage{eledmac}
\usepackage{times, ulem, verse, setspace}
\renewcommand{\rmdefault}{ptm}

\newcommand{\A}{\Afootnote}
\newcommand{\B}{\Bfootnote}
\newcommand{\edt}{\edtext}
\newcommand{\I}{\textit}
\newcommand{\U}{\uline}
\newcommand{\OED}{(\I{OED})}
\newcommand{\CL}{\I{CL}}
\newcommand{\CT}{(comma tail removed) H}
\newcommand{\PE}{(paragraph ends) }
 \newcommand{\D}{\ldots}

\setcounter{page}{8}
\setcounter{firstlinenum}{0}
\setlength\parindent{11pt}
\renewcommand*{\thefootnoteA}{\alph{footnoteA}}
\renewcommand{\notenumfont}{\bfseries\footnotesize}
\renewcommand*{\thefootnoteB}{\alph{footnoteB}}
\renewcommand{\notenumfont}{\bfseries\footnotesize}
\footparagraph{A}
\footparagraphX{B}
\frenchspacing
\noendnotes

\begin{document}
\beginnumbering
\pstart

\begin{flushright}
\edt{\edt{\I{Rotterdam}}{\B{a prosperous Dutch port.}}, Friday, \edt{Aug.
3}{\B{Plans kept changing.  \I{The Flying Post or The Post Master}, 1716
Apr. 14: ``Mr. Wortley Montague, late one of the Lords of the Treasury, is
going Ambassador to Constantinople, in the Room of Colonel Sutton, who has
obtain'd Leave to come Home."  Jul. 3, office circular: ``Mr. Montague,
being appointed to succeed Sir Robert Sutton as his Majesty's ambassador at
the Ottoman Port, a man-of-war is ordered to convey him to Constantinople"
(Polwarth, 1:36).  Jul. 7: ``The honourable Edward Wortley, alias Montague,
will set forward this Week on his Embassy to Constantinople"; ``Edward
Wortley, alias Montague, Esq; Ambassador Extraordinary to the Ottoman
Porte, sets out in a few Days for Constantinople, to relieve Sir Robert
Sutton" (\I{Shift Shifted}; \I{Weekly Journal or British Gazetteer}). Jul.
27, John Robethon (d. 1722, secretary to George I) to Alexander Hume
Campbell, Lord Polwarth (1675--1740, ambassador-extraordinary to
Copenhagen): ``The Danish ambassador left in one of the King's yachts for
Holland on his way to Hanover this morning, and at the same time Mr.
Wortley Montagu left in another yacht also for Holland, whence he proceeds
by land to Constantinople" (\I{Polwarth}, 1:47).  Jul. 28: ``Edward-Wortley
Montague, Esq; set out Yesterday Morning on his Embassy to Constantinople"
(\I{Weekly Packet}).  Jul. 31, office circular enclosure: ``Mr. Wortley
Montague, his Majesty's ambassador extraordinary to Constantinople, sets
out to-morrow to begin his journey thither" (\I{Polwarth},1:49).  Aug. 3,
office circular: ``Last Wednesday being the anniversary of his Majesty's
happy accession to the throne \ldots.The same day Mr. Wortley Montagu set
out for his embassy \ldots " (\I{Polwarth}, 1:52).  A man-of-war was the
largest and most-heavily armed sailing ship in the British navy; for yacht,
see l.8n.}}. \edt{O.S.}{\B{To convert from old-style British dates to
new-style (European) Continental dates,  add eleven days to the British
date.  Where needed for quick referencing, both dates are supplied [using
brackets].}} 1716.}{\lemma{\I{Rotterdam}\D1716.}\A{Rotterdam, Friday
Aug\textsuperscript{t} 3. O.S. H}}
\end{flushright}
\pend
\endnumbering

\end{document}