Your problem is quite complex to solve. I have found a way for eledmac (thank!) and for your specific problem with your MWE.

The problem is that adding space after the rule is problematic, because TeX doen't count this space as a space for notes. That's why it can override the line number.

The solution is quite complex, and need TeX knowledge.

A footnote is a TeX insert. For each TeX type of insert, there are three parameters :

- a) length which is kept in the page only if a insertion is made. In your case, only if at least one \footnote is called.
- b) length which say the maximum height all inserts can have in the same page.
- c) factor which is used when a insertion is added, (ie a footnote in your case) which determines the height of the insertion. When the total of insertion*factor > b, the insert is full, and tex output it (to summarize).

If you change the a) length to add your kern after rule, it will solve the problem, because the space will be "reserved" by TeX in the total height of the notes. This a length is, with your package, equal to \footdimen.

So, if you change `\footin`, you will say to TeX to kept this space before printing insertion.

But, the problem is that `\MFL@joinrule`,  the command called by `manyfoot` when printing extra footnotes rule use `\footin` to add space before the rule. So the space you want after the rule will be also add before the rule! The same is also true for `\make@cols` which is called by LaTeX and print the first rule in the series.

The solution is to patch `\MFL@joinrule` and `\make@cols` to delete this space before the rule, because it is the space after the rule.


We can do it with etoolbox (which is loaded by polyglossia)

So code for your preamble :

    \makeatletter
    \newcommand{\before}{5.52pt}%Space before rule
    \newcommand{\after}{10.52pt}% Space after rule
    \renewcommand{\footnoterule}{%Redefine footnoterule
      \hrule width 3cm
      \kern \after}
    % Change the space kept for rules+spaces around
    \advance\skip\footins by \after
    \advance\skip\footins by \before
    % Not print the after space before the rule
    \patchcmd{\@makecol}{\vskip \skip\footins}{\vskip \skip\footins\vskip-\after}{}{}
    %load parafootskip
    \usepackage[ruled,para]{manyfoot}
        % Not print the after space before the rule
    \patchcmd{\MFL@joinrule}{\@tempskipa\skip#5}{\@tempskipa\skip#5\advance\@tempskipa by -\after}{}{}
    \makeatother

But i think, indeed, that for next edition, you should look at eledmac. 